\begin{thebibliography}{200}

%Application Notes
\bibitem{ACD} Antenna Circuit Design for RFID Applications, AN710.
\bibitem{ADN} HF Antenna Design Notes, Literature Number: 11-08-26-003.
\bibitem{HFACB} HF Antenna Cook Book, Lit. Number 11-08-26-001.
\bibitem{MRICF} Micore Reader IC Family; Directly Matched Antenna Design, Rev. 2.05, 10 May 2006.
\bibitem{RFIDPA} Mifare®(14443A) 13,56 MHz RFID Proximity Antennas, Application Note.

\bibitem{} MIFARE Type Identification Procedure; AN10833 Rev. 3.1 — 07 July 2009.
\bibitem{} MIFARE ISO/IEC 14443 PICC Selection; AN10834 Rev. 3.0 — 26 June 2009.
\bibitem{} MIFARE Classic Commands; AN10856 Rev. 1.0 — 31 July 2009.
\bibitem{} MIFARE and handling of UIDs; AN10927 Rev. 2.0 — 01 September 2010.
\bibitem{} Mainstream contactless smart card IC for fast and easy; MF1S5009 Rev. 3 — 27 July 2010.
\bibitem{} MIFARE Standard Card IC MF1 IC S50 Functional Specification; Revision 5.1 May 2001.

%Hojas de datos
\bibitem{RC632} MIFARE® and I Code CL RC632 Multiple protocol contactless reader IC.
\bibitem{HD_VLT} 8-BIT BIDIRECTIONAL VOLTAGE-LEVEL TRANSLATOR.
\bibitem{dpy} HD44780U (LCD-II), Dot Matrix Liquid Crystal Display Controller/Driver, Rev. 0.0 1998. 
\bibitem{LDO} LM1117/LM1117I 800mA Low-Dropout Linear Regulator.
\bibitem{LCM} LCM-S01602DSF/A - hoja de datos del LCD16x2.
\bibitem{manualBb} BeagleBoard System Reference Manual Rev C4, Revision 0.0.

%HandBooks
\bibitem{SCHb} Smart Card Handbook, Third Edition, Wolfgang Rankl and Wolfgang Effing, 2003, ISBN: 0-470-85668-8. 
\bibitem{RFIDHb} RFID Handbook: Fundamentals and Applications in Contactless Smart Cards and Identification,
Second Edition, Klaus Finkenzeller, 2003, ISBN: 0-470-84402-7. 


\bibitem {Attack} A Practical Attack on the MIFARE Classic, Gerhard de Koning Gans, Jaap-Henk Hoepman and Flavio D. Garcia, 2008.

%Angström
\bibitem{AngManual} Angström Manual - Embedded Power -, Luca Merciadri and Kooi Koën, 29 June 2010.


%CT/API cap-6
\bibitem{ctapi} Application Independent CardTerminal Application Programming Interface for ICC Applications; 
Deutsche Telekom AG / PZ Telesec, GMD - Forschungszentrum Informationstechnik GmbH, TÜV Informationstechnik GmbH, TELETRUST Deutschland e.V., 30.10.1996.
%CT/BCS cap-6
\bibitem{ctbcs} Application independent CardTerminal Basic Command Set for ICC applications; 
TeleTrusT Deutschland e.V., GMD Forschungszentrum Informationstechnik GmbH, Version 0.9, 28.07.1995.
%IFDhandler
\bibitem{ifdhandler} IFDHandler 3.0 MUSCLE PC/SC IFD Driver API; David Corcoran \& Ludovic Rousseau, July 28, 2004.


%Libros
\bibitem{KiCad} Diseño y desarrollo de circuitos impresos con KiCad, Miguel Pareja Aparicio, 2010, ISBN: 978-84-937769-1-6.
\bibitem{} El lenguaje de programación C, Brian W. Kernighan y Dennis M. Ritchie, 1991, ISBN: 968-880-205-0.

%Normas ISO
\bibitem{7816} Norma ISO/IEC 7816.
\bibitem{14443} Norma ISO/IEC 14443.


%LINKS
\bibitem{OpenPCD} OpenPCD, http://www.openpcd.org/, agosto 2011.
\bibitem{librfid} librfid, http://openmrtd.org/projects/librfid/, agosto 2011.
\bibitem{9G20} GES9G20, http://www.glomationinc.com/product\_9G20.html, agosto 2011.
\bibitem{Hawk} Hawkboard, http://www.hawkboard.org/, agosto 2011.
\bibitem{Beagle} Página oficial Beagleboard, http://beagleboard.org/, agosto 2011.
\bibitem{foroBb} Foro de Beagleboard, https://groups.google.com/forum/\#!forum/beagleboard, agosto 2011.
\bibitem{consumo1} Consumo de Beagleboard, http://elinux.org/BeagleBoardFAQ\#Power\_usage, \\
agosto 2011.
\bibitem{consumo2} Consumo de Beagleboard, http://www.h-online.com/news/forum/S-Power-\\
consumption-under-2W/forum-110345/msg-14369911/read/, agosto 2011.
\bibitem{rec} Recuperación Beagleboard, http://elinux.org/BeagleBoardRecovery, agosto 2011.
\bibitem{rec1} Recuperación Beagleboard, http://elinux.org/BeagleBoardNAND, agosto 2011.
\bibitem{OE-Bb} Openembedded-Bitbake, http://wiki.openembedded.net/index.php/BitBake\_\%28
dev\%29, agosto 2011.
\bibitem{KiCad} KiCad, http://www.lis.inpg.fr/realise\_au\_lis/kicad/, agosto 2011.
\bibitem{gEDA} gEDA, http://www.gpleda.org/index.html, agosto 2011.
\bibitem{subversion} Subversion, http://subversion.apache.org/, agosto 2011.
\bibitem{git} Git, http://git-scm.com/, agosto 2011.
\bibitem{geany} Geany, http://www.geany.org/, agosto 2011.
\bibitem{minicom} minicom, http://alioth.debian.org/projects/minicom/, agosto 2011.
\bibitem{Proxmark} Proxmark, http://www.proxmark.org/proxmark, agosto 2011.
\bibitem{Angs} Angström, http://www.angstrom-distribution.org/, agosto 2011.
\bibitem{Angs_MLO} MLO, http://www.angstrom-distribution.org/demo/beagleboard/MLO/, agosto 2011.
\bibitem{Narc} Narcissus, http://narcissus.angstrom-distribution.org/, agosto 2011.
\bibitem{termios} termios, http://pubs.opengroup.org/onlinepubs/007908799/xsh/termios.h.html, agosto 2011.
\bibitem{linuxBoot} Proceso de booteo de linux, http://www.ibm.com/developerworks/linux/library/
l-linuxboot/index.html, agosto 2011.
\bibitem{Make} Make, http://es.wikipedia.org/wiki/Make, agosto 2011.
\bibitem{DDD} DDD, http://www.gnu.org/s/ddd/, agosto 2011.
\bibitem{gpio} GPIO, http://www.avrfreaks.net/wiki/index.php/Documentation:Linux/GPIO\#
Interfaces\_explained, agosto 2011.
\bibitem{gpioK} Kernel GPIO, http://kernel.org/doc/Documentation/gpio.txt, agosto 2011.
\bibitem{conf_SDK} Configuración SDK, http://www.electronsonradio.com/2011/04/intro-to-basic-cross-compiling-for-the-beagleboard/, agosto 2011.
\bibitem{mina} Grupo mina - INCO, http://www.fing.edu.uy/inco/grupos/mina/, agosto 2011.
\bibitem{lcd4linux} LCD4Linux, http://ssl.bulix.org/projects/lcd4linux/, agosto 2011.
\bibitem{ForoTI} Foro Texas Instruments, http://e2e.ti.com/support/interface/etc\_interface/f/391/t/\\
114719.aspx, agosto 2011.
\bibitem{Audiofingerprint} Audiofingerprint, http://iie.fing.edu.uy/cursos/file.php/14/proyectos/2009/\\
audio\_fingerprint/index.html, agosto 2011.
\bibitem {Wikisc} Tarjetas inteligentes, http://es.wikipedia.org/wiki/Tarjeta\_inteligente, agosto 2011.

%links Daniel
\bibitem{} Beagleboards beginners, https://groups.google.com/forum/\#!forum/beagleboard, agosto 2011.

\bibitem{} Desarrollo en Beagleboard, http://members.cox.net/ebrombaugh1/embedded/
beagle/index.html, agosto 2011.

\bibitem{} Wiki Beagleboard, http://code.google.com/p/beagleboard/w/list, agosto 2011.

\bibitem{} NAND de la Beagleboard, http://elinux.org/BeagleBoardNAND, agosto 2011.

\bibitem{} Crosscompilación en Beagleboard, http://garrenblog.blogspot.com/2008/10/adven
tures-in-beagleboard-land-compiler.html, agosto 2011.

\bibitem{} Primeros pasos Beagleboard, http://www.mipixel.com/electronica/beagleboard, agosto 2011.

\bibitem{} Arranque de Linux en la Beagleboard, http://www.ibm.com/developerworks/libra
ry/l-beagle-board/index.html, agosto 2011.

\bibitem{} Internet en Beagleboard, http://thoughtshubham.blogspot.com/2010/03/internet-over-usb-otg-on-beagleboard.html, agosto 2011.

\bibitem{} OpenEmbedded en Ubuntu 10.04, http://maltanar.blogspot.com/2010/05/open
embedded-on-ubuntu-1004.html, agosto 2011.

\bibitem{} Solución de problemas con Beagleboard, http://www.electronsonradio.com/cate
gory/bb/, agosto 2011.

\bibitem{} Foro Beagleboard - Testeo SPI, http://groups.google.com/group/beagleboard/
browse\_thread/thread/d6a4e0703033cada\%7CSPI, agosto 2011.

\bibitem{} SPI en Beagleboard, http://elinux.org/BeagleBoard/SPI, agosto 2011.

\bibitem{} Parche SPI en Beagleboard con kernel 2.6.32, http://elinux.org/BeagleBoard/
SPIPatch-2.6.32, agosto 2011.

\bibitem{} Foro Beagleboard – SPI, https://groups.google.com/forum/\#!topic/beagleboard/
p7Ua8jmILkM, agosto 2011.

\bibitem{} Foro Beagleboard - Configuración SPI, https://groups.google.com/forum/\#!topic/
beagleboard/QpiPDhTbDwE, agosto 2011.

\bibitem{} Foro Beagleboard - Configuración SPI, https://groups.google.com/forum/\#!topic/
beagleboard/3v3qsRQNQzA, agosto 2011.

\bibitem{} Foro Beagleboard - Aplicar parche SPI, https://groups.google.com/forum/
\#!searchin/beagleboard/\%22bitbake\$20-c\$20rebuild\%22/beagleboard/TF6TCJx
XL1Y/joHWHlxiPZEJ, agosto 2011.

\bibitem{} Foro Beagleboard - SPI en Beagleboard, https://groups.google.com/forum/
\#!searchin/beagleboard/applying\$20patches/beagleboard/s340Ss-GoJU/
KAeSfH8vqb8J, agosto 2011.

\bibitem{} Foro Beagleboard - Problemas con SPI, https://groups.google.com/forum/?show
\_docid=9db5bcf44392d4a0\#!topic/beagleboard/MgzrowFy-6U, agosto 2011.

\bibitem{} Foro Beagleboard - Construyendo un kernel y habilitar SPI, https://groups.
google.com/forum/\#!topic/beagleboard/XrMz-9Byum0, agosto 2011.

\bibitem{} Foro Beagleboard - SPI en Beagleboard, https://groups.google.com/forum/
\#!topic/beagleboard/s340Ss-GoJU, agosto 2011.

\bibitem{} Foro Beagleboard - Compilación de kernel, https://groups.google.com/forum/
?pli=1\#!searchin/beagleboard/mkimage/beagleboard/Od\_tCEHwUvk/DxoPO8Y
v9t0J, agosto 2011.

\bibitem{} Foro Beagleboard - Problemas construyendo uImage, https://groups.google.com/
forum/?pli=1\#!msg/beagleboard/MDxilRJKIIQ/r0RVzZdIdYsJ, agosto 2011.

\bibitem{} Foro Beagleboard - Sobre las versiones generadas de uImage, https://groups.
google.com/forum/\#!topic/beagleboard/DR-ruujKu9U, agosto 2011.

\bibitem{} Foro Beagleboard - Aplicar parche al kernel linux, https://groups.google.com/\\
forum/\#!searchin/beagleboard/applying\$20patches/beagleboard/bAjYSVKAyAM/
jCTXlbfn40wJ, agosto 2011.

\bibitem{} Openmbedded, http://www.openembedded.org/index.php/Main\_Page, agosto 2011.

\bibitem{} OpenEmbedded , uso, http://www.uv-ac.de/openembedded/, agosto 2011.

\bibitem{} Foro Beagleboard - configuración de kernel con OpenEmbedded, https://groups.
google.com/forum/\#!msg/beagleboard/UlL4e0\_O\_UE/\_NefIFsj7pkJ, agosto 2011.

\bibitem{} Bitbake, tutorial, http://www.gumstix.org/software-development/open-embedded
/160-bitbake-tutorial.html, agosto 2011.

\bibitem{} Bitbake, tutorial, http://bitbake.berlios.de/manual/, agosto 2011.

\bibitem{} Foro Beagleboard - OpenEmbedded/Bitbake, como forzar regeneración de \\
uImage, https://groups.google.com/forum/?pli=1\#!searchin/beagleboard/uimage/
beagleboard/FibI\_LXNVGk/mNHp6ZPNOAYJ, agosto 2011.

\bibitem{} Foro Beagleboard - U-boot, fuentes, https://groups.google.com/forum/\#!searchin/
beagleboard/u-boot\$20source/beagleboard/XD82Fd54ABg/xCUaE5W\_OwQJ, agosto 2011.

\bibitem{} Beagleboard, desarrollo de software, http://wh1t3s.com/tag/beagleboard/, agosto 2011.

\bibitem{} Foro Beagleboard - Línea de 1.8V en el bloque de expansión, https://groups.\\
google.com/forum/\#!topic/beagleboard/00urlSRNrXA, agosto 2011.

\bibitem{} PinMux en el bloque de expansión, http://elinux.org/BeagleBoardPinMux, agosto 2011.

\bibitem{} Guía de programación Serial, http://www.easysw.com/$\sim$mike/serial/serial.html, agosto 2011.

\bibitem{} Chequear y utilizar puertos seriales bajo Linux, http://www.cyberciti.biz/faq/find-out-linux-serial-ports-with-setserial/, agosto 2011.

\bibitem{} Programación Serial, http://tldp.org/HOWTO/Serial-Programming-HOWTO/\\
x115.html, agosto 2011.

\bibitem{} Programación Serial, http://www.linux.com/learn/docs/ldp/745-Serial-Progra\\
mming-HOWTO, agosto 2011.

\bibitem{} Interfaz GPIO, http://www.avrfreaks.net/wiki/index.php/Documentation:Linux/GPIO, agosto 2011.

\bibitem{} Encendido y apagado de pines de la Beagleboard, http://blog.makezine.com/\\
archive/2009/02/blinking-leds-with-the-beagle-board.html?CMP=OTC-0D6B48984890, agosto 2011.

\bibitem{} Uso de diff y patch, http://www.linuxtutorialblog.com/post/introduction-using-diff-and-patch-tutorial, agosto 2011.

\bibitem{} CodeSourcery 2009q3-67, http://www.codesourcery.com/sgpp/lite/arm/portal/\\
release1039, agosto 2011.

\bibitem{} Librfid, instalación, http://wiki.yobi.be/wiki/RFID\#librfid, agosto 2011.

\bibitem{} Proyectos con Beagleboard, http://www.hy-research.com/projects.html, agosto 2011.

%fin de links Daniel



%links sobre pcsc
\bibitem{pcsclite} PCSC-Lite, http://pcsclite.alioth.debian.org/, agosto 2011.
\bibitem{pcsclite_esp} PCSC Workgroup, http://www.pcscworkgroup.com/, agosto 2011.
\bibitem{pcsc/ccid_down} Descargas PCSC-Lite, https://alioth.debian.org/frs/?group\_id=30105, agosto 2011.
\bibitem{pcsctools_down} http://ludovic.rousseau.free.fr/softwares/pcsc-tools/, agosto 2011.

\bibitem{} Blog de Ludovic Rousseau - autor de PCSC-Lite, http://ludovicrousseau.blogspot.com/, agosto 2011.

%empresas compras
\bibitem{Nw} Newark, http://www.newark.com/, agosto 2011.
\bibitem{Dk} Digikey, http://www.digikey.com/, agosto 2011.
\bibitem{SpeCom} Special Computing, http://specialcomp.com/, agosto 2011.
\end{thebibliography}
